---
title: "Bonus: R and Python Integration"
author: "Abhishek Prakash Sharma"
date: "2026-09-27"
---

This post demonstrates passing data between R and Python using the `reticulate` package in a single Quarto document.

## Setup

First, we load `reticulate` and point it to the project's `uv` virtual environment so it uses the correct Python installation.

```{r}
#| message: false
#| warning: false
library(reticulate)
use_virtualenv("../../.venv", required = TRUE)
```

## Create Data in Python

Let's generate a simple Pandas DataFrame in Python. Notice how we use `{python}` to tell Quarto to switch languages here.

```{python}
import pandas as pd

python_data = {
    'species': ['Adelie', 'Chinstrap', 'Gentoo'],
    'count': [152, 68, 124]
}
python_df = pd.DataFrame(python_data)
print(python_df)
```

```{r}
#| message: false
#| warning: false
#| label: fig-bonus-plot
#| fig-cap: "Penguin counts by species, plotted in R from Python data."
library(ggplot2)

# Access the Python object
r_df <- py$python_df

ggplot(r_df, aes(x = species, y = count, fill = species)) +
  geom_col() +
  theme_minimal() +
  labs(title = "Penguin Counts (Data from Python, Plot from R)",
       x = "Species", y = "Count")
```